---
title: "Analysis of Crime Data_v1"
author: "Fiona Chin"
date: "October 15, 2016"
output: html_document
---

# Hello This is the first analysis of the data!  We made stuff happen.
So our goal is to see how to predict crime incidents.)

```{r echo=FALSE, include=FALSE, cache=FALSE}
#Must install packages first using install.packages("insert_package_name")
library(readr)
library(randomForest)
library(caret)
library(ggplot2)
library(dplyr)
library(stringr)
library(corrplot)

set.seed(231)
#Navigating through directory
setwd("/Users/fi/Documents/GitHub/Predicting-Crimes-in-Philadelphia") # Set own path

#Importing data in two different ways 
train <- read.csv("crime.csv", stringsAsFactors=FALSE)

#For the time being, Lets remove the NA rows so we can see the basic relationships
train2 = train[complete.cases(train),]
nrow(train2)

```

## General Histograms

### Police Service Area Histogram

```{r, echo=FALSE, cache=FALSE, warning=FALSE, message=FALSE}
ggplot(train,aes(x = Psa)) + geom_bar()
```
We can say that majority of the crime occurs in regions 1, 2, and 3.  Lets remove the number regions since I think regions A through Z indicate sub-regions of 1, 2, 3, and 4???

```{r, echo=FALSE, cache=FALSE, warning=FALSE, message=FALSE}
train3 = filter(train, Psa != 1 & Psa != 2 & Psa != 3 & Psa != 4)
ggplot(train3,aes(x = Psa)) + geom_bar()
```
We should figure out what regions T to Z are since they have the lowest count of crimes (not specified by type of crime yet)

### Hour
The time for crime is in Philadelphia occurs:
```{r, echo=FALSE, cache=FALSE, warning=FALSE, message=FALSE}
ggplot(train,aes(x =Hour)) + geom_bar()
```

## Ok Let's start with a really complicated Correlation Analysis
This really doesn't tell us new information because the features that have strong relationships logically make sense. 
```{r, echo=FALSE}
#Correlation Matrix
M <- cor(train2[sapply(train, function(x) !is.character(x))]) 
corrplot(M, method = "number", order = "hclust",type='lower', diag=F, addCoefasPercent=T, )


```


## Have to clean data and separate in terms of time and date





